\documentclass[sigconf,screen]{acmart}
% For algorithms in ACM template
\makeatletter
\newif\if@restonecol
\makeatother
\let\algorithm\relax
\let\endalgorithm\relax
\usepackage[T1]{fontenc} 
\usepackage[subtle]{savetrees}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{cleveref}
\usepackage{makecell}
\usepackage{soul}
\usepackage{tabularx}
\usepackage{enumitem}
\providecommand\algorithmname{algorithm}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\begin{document}

\title{Testing Approximations for Augmented and Virtual Reality}

\author{Samuel Grayson}
\email{grayson5@illinois.edu}
\affiliation{%
  \institution{University of Illinois at Urbana-Champaign}
}

\author{Navi Ning}
\email{xning5@illinois.edu}
\affiliation{%
  \institution{University of Illinois at Urbana-Champaign}
}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column

\newcommand{\todo}[1]{\textcolor{red}{#1}}

\begin{abstract}
AR/VR systems have stringent realtime performance, power, and area constraints, which are difficult to simulatenously satisfy.
One way to bring this difficulty down is through the use of \textit{approximation techniques};
    in many cases, the output only has to fool a human, so the algorithms can be simplified or reduced.
However, one does not know \textit{a priori} which approximations will `fool the human.'
This project seeks automataically determine the acceptability of approximations, so approximation-configurations can be rapidly searched.
\end{abstract}

% http://dl.acm.org/ccs.cfm
% \begin{CCSXML}
% <ccs2012>
% <concept>
% <concept_id>10011007.10010940.10010992.10010993.10010994</concept_id>
% <concept_desc>Software and its engineering~Functionality</concept_desc>
% <concept_significance>300</concept_significance>
% </concept>
% </ccs2012>
% \end{CCSXML}

% \ccsdesc[300]{Software and its engineering~Functionality}

% \keywords{approximation tuning}

\maketitle

\input{introduction}
\input{implementation}
\input{conclusion}

% \begin{acks}
% We would like to acknowledge the ILLIXR group at the University of Illinois at Urbana-Champaign for the ILLIXR research platform itself and timely support. Specifically, we would like to thank Boyuan Tian and Yihan Pang for helping with the trajectory alignment and Muhammed Huzaifa for the coordinate transformation.
% \end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{main}

\appendix
\section{Pre-existing and Concurrent Work}
This work was \textit{not} done for this project:

\begin{itemize}
\item OpenVINS already had tunable parameters.
\item ILLIXR already had timing infrastructure, but it was insufficient for our purposes, because it could not be adapted to time \textit{inside} OpenVINS.
\item The ILLIXR research group had already considered using SSIM, but their implementation was not ready at the time we needed one, so we implemented it ourselves. We could not upstream our implementation because theirs is able to handle a wider class of applications.
\item The ILLIXR research group helped me find and use Umayama's Method for aligning the pose.
\end{itemize}

This work was for this project:

\begin{itemize}
\item We designed and implemented a the infrastructure for configuring approximations across all of ILLIXR (not just OpenVINS).
\item We rewrote the timing infrastructure (from scratch).
\item We implemented component-level metrics.
\item We implemented the coordinate transformation code.
\item We implemented our own version of system-level metric (apitrace, SSIM, homography-distance).
\item We designed and implemented our own video metric (homography-distance).
\item We explored the idea of a estimating system-error by component-level proxy specifically for this projet.
\end{itemize}

\section{Total Effort}

We spent about 150 hours on this project collectively.

See our changes in ILLIXR:
\url{https://github.com/ILLIXR/ILLIXR/compare/illixr-testing?expand=1}.

See our changes in OpenVINS:
\url{https://github.com/ILLIXR/open\_vins/compare/realsense...ILLIXR:illixr-testing?expand=1}.

Note that the first few commits in our OpenVINS branch are not ours, since we merged with upsteram.

\section{Progress 6 Report}

Since progress report 5, we:

\begin{itemize}
\item designed and implemented a homography-distance.
\item designed and implemented timing infrastructure.
\item analyzed and visualized the data collected from our experiments (timing, component-level distance).
\end{itemize}

\end{document}
\endinput
